Various examples of cdf plots

### 2017-01-03 analysis/plot_cdf_eg.Rmd
Successfully rendered plot_cdf_eg.Rmd, but only after dropping the 'big-normal' scenarios from the plots; it seems that the big-normal results are no longer included.

TO DO: Explain here what this chunk does.

@@

  if (df$method == "truth"){
    s    = dsc$scenarios[[df$scenario]]
    galt = s$args$g
    g    = normalmix(c(pi0,(1 - pi0) * mixprop(galt)),
                     c(0,comp_mean(galt)),
                     c(0,comp_sd(galt)))
  } else {
    if (grepl("mixfdr",df$method)) {
      temp$output$fitted_g = mixfdr2fitted.g(temp$output)$fitted.g
    }
    g = temp$output$fitted_g
  }
  return(data.frame(x = x,y = as.numeric(mixcdf(g,x)),pi0 = pi0))
}

@@

TO DO: Explain here what this chunk does.

@@

TO DO: Explain here what this chunk does.

@@

TO DO: Explain here what this chunk does.

@@

TO DO: Explain here what this chunk does.

@@

TO DO: Explain here what this chunk does.

@@

I wanted to add the npmle to the plot...

TO DO (maybe): Add more details here about this chunk?

```{r egcdf-reduce-with-npmle, dev='pdf',fig.height=4.5, fig.width=6, crop=TRUE}
run_nplme = function(SEED = 1,
                     PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew",
                                       "big-normal","bimodal")) {
  df = data.frame(seed = NULL,scenario = NULL,method = NULL,x = NULL,
                  y = NULL,pi0 = NULL)
  for(SCENARIO in PLOTSCENARIOS) {
    temp = load_example(dsc_shrink,SEED,SCENARIO,"ash.n","../output/dsc-shrink-files/")
    z    = GLmix(temp$input$betahat)
    df = rbind(df,data.frame(seed = SEED,scenario = SCENARIO,method = "NPMLE",
                             x = z$x,y = cumsum(z$y)/sum(z$y),pi0 = NA))
  }
  return(df)
}

plot_mean_cdf_with_npmle = 
  function(SEED          = 1,
           PLOTMETHODS   = c("ash.n","ash.u","ash.hu","truth","mixfdr.tnull"),
           PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew",
                             "big-normal","bimodal"),
           pi0filter     = FALSE,...) {
  if (length(SEED) > 1)
    stop("plot with npmle only implemented for a single seed")
  PLOTNAMES = PLOTSCENARIOS

@@

  df.npmle = run_nplme(SEED, PLOTSCENARIOS)
  df.cdf   = rbind(df.cdf,df.npmle)

@@

plot_mean_cdf_with_npmle(1,PLOTMETHODS = c("truth","ash.hu"),
                         PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew",
                                           "big-normal","bimodal")) + 
  facet_wrap(~ scenario, nrow = 2)
```

>>>>

Define a couple functions that compile CDF data in such a way that it is 
easy to plot the CDFs using ggplot2.

@@

  if (df$method == "truth") {
    s    = dsc$scenarios[[df$scenario]]
    galt = s$args$g
    g    = normalmix(c(pi0,(1 - pi0) * mixprop(galt)),
                     c(0,comp_mean(galt)),
                     c(0,comp_sd(galt)))
  } else {
    if (grepl("mixfdr",df$method)) {
      temp$output$fitted_g = mixfdr2fitted.g(temp$output)$fitted.g
    }
    g = temp$output$fitted_g
  }
  return(data.frame(x = x,y = as.numeric(mixcdf(g,x)),pi0 = pi0))
}

@@

Show the CDFs for all methods and all scenarios, based on a single data set.

@@

Show the CDFs for all scenarios, this time averaged over 100 simulated data 
sets.

@@

Same as above, but with custom colours.

@@

Same as above, but this time the CDFs are averaged over 100 simulated data sets.

@@

Now with custom colours.

@@

I wanted to add the npmle method (fit using the GLmix function) to the plot...

```{r egcdf-reduce-with-npmle, dev='pdf',fig.height=4.5, fig.width=6, crop=TRUE}
run_nplme = function (SEED = 1,PLOTSCENARIOS = c("spiky","near-normal",
                                                 "flat-top","skew","bimodal")) {
  df = data.frame(seed = NULL,scenario = NULL,method = NULL,x = NULL,
                  y = NULL,pi0 = NULL)
  for (SCENARIO in PLOTSCENARIOS) {
    temp = load_example(dsc_shrink,SEED,SCENARIO,"ash.n","../output/dsc-shrink-files/")
    z    = GLmix(temp$input$betahat)
    df   = rbind(df,data.frame(seed = SEED,scenario = SCENARIO,method = "NPMLE",
                               x = z$x,y = cumsum(z$y)/sum(z$y),pi0 = NA))
  }
  return(df)
}

plot_mean_cdf_with_npmle = 
  function(SEED          = 1,
           PLOTMETHODS   = c("ash.n","ash.u","ash.hu","truth","mixfdr.tnull"),
           PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","bimodal"),
           pi0filter     = FALSE,...) {
  if (length(SEED) > 1)
    stop("plot with npmle only implemented for a single seed")
  PLOTNAMES = PLOTSCENARIOS

@@

  df.npmle = run_nplme(SEED,PLOTSCENARIOS)
  df.cdf   = rbind(df.cdf,df.npmle)

@@

plot_mean_cdf_with_npmle(1,PLOTMETHODS = c("ash.hu","truth"),
                         PLOTSCENARIOS = c("spiky","near-normal","flat-top",
                                           "skew","bimodal")) +
  facet_wrap(~ scenario, nrow = 2)
```
